\section{Product evaluation}
All parts of the process have been discussed, and it is now time to review the quality of the finished product. Considering all factors discussed so far in this chapter, the team was content with the final product. The finished product consists of the Android app, the server and documentation for both, and lastly this report. As with most projects though, the team wishes it had accomplished more of its goals. There is some functionality the team would have like to completed given different circumstances. The team would also like to one day see the app fully developed with hardware components that allow for automatic measurement and control, but the team were comfortable admitting this was out of reach within the bounds of this project. 

The customer was very pleased with the finished product. As previously mentioned, the team cooperated very closely with the customer and therefore he knew pretty accurately which state the project would be in at product delivery. The customer wants to integrate the project in the work the SINTEF team has already done for the CoSSMic project. The customer also gave the team motivation towards commercializing the app. A customer approval letter was given by the customer to include in this report. This can be found in appendix~\ref{sec:recommendation}.

The last contact with the customer was done as a presentation to SINTEF Energy and the the people working in CoSSMic. After having presented the product, the team had a more in depth discussion with the CoSSMic team on how they had solved the different issues related to creating the entire solution. 
