\chapter{Project Management}
<<<<<<< HEAD
The object of this chapter is to provide information about the project management and give an overview of the project's process. 

The first part of the chapter consists of a description of which development methods the team used and why we chose them. The second part consists of an overview of the project time allocation, including a work breakdown structure, which gives an overview of which tasks the project consists of, and a Gantt diagram, which briefly explains the time line of the project's progress. The last part consists of a analysis of risk that might occur during the project.
=======
The object of this chapter is to provide information about the project management methods used in this project. And \todo[inline]{give an overview of the project's process. <-- Is this not supposed to be in the development process chapter?} 
>>>>>>> c525ebfdd6aa59327f08d6c54b2119b63058db4c

The first part of the chapter consists of a description of which development methods the team used and why they were chosen. The second part consists of an overview of the project time allocation, including a work breakdown structure, which gives an overview of which tasks the project consists of, and a Gantt diagram, which briefly explains the time line of the project's progress. The last part consists of a risk analysis and a thorough explanation on the thought behind each of them.

\todo[inline]{The section about agile development is not very consistent in the use of we and past tense. This must be fixed}
\input ch/projectManagement/sec/agileDevelopment.tex
\input ch/projectManagement/sec/scrum.tex
\newpage
\input ch/projectManagement/sec/extremeProgramming.tex
\input ch/projectManagement/sec/wbs.tex
\input ch/projectManagement/sec/gantt.tex
\input ch/projectManagement/sec/risk.tex