\section{Testing non-functional requirements}
\label{sec:testingnonfunctionalrequirements}
Non-functional requirements are requirements representing the overall usability and quality of the application. To test these requirements different kinds of usability tests were performed.

\subsection{Usability testing}
\label{sec:userTest}
Usability testing is a technique used to evaluate an application by testing it on actual users, preferable within the applications target audience and with different backgrounds and with a different level of technical understanding. This kind of tests gives the developers a better understanding of how the common users react to specific features in the application. If they struggle with, or are unable to complete certain tasks, some changes in the graphical user interface might be necessary.
The target user group for the application is home owners. This is a wide target audience that puts serious requirements on the applications usability. To test this usability we used two different methods, as described in the subsequent sections.

\subsubsection{Hallway testing}
Hallway testing is a typical method for usability testing~\cite{hallwaytesting}. In hallway testing, the testers are a small group of random people (''people who pass by in the hallway,'' hence the name). During the test, the testers are given a set of tasks to perform while the developers observe how they perform their given tasks. This allows the developers to make some choices early in the development process without the need for protracted user testing with carefully selected users. 
The team used this method to some degree, mostly in the early stages of prototyping.

\subsubsection{Remote usability testing}
%When the developers and test subjects find themselves separated by long distance, conducting a usability test might arise some unforeseen challenges.

%For instance, the remote testing may lack the immediacy and sense of ''presence'' that often is desired to support a collaborative testing process. It may also include having reduced control over the testing environment

By using remote usability testing~\cite{remoteTest}, the team was able to get input and opinions from users closer to the applications target audience.
The tests were conducted mainly on friends and relatives. The testers were given the application and a set of tasks. When the tests had been performed, the testers filled out a simple form where they rated the usability of the application. The form was then used to make improvements on the applications user-interface.

\subsection{Performing the tests}
The project had two main requirements to cover the overall usability of the application. The following paragraphs describes how these were tested.

\subsubsection{NFR1: The application should be easy to use}
The target audience of this application does not necessarily have any technical insight. This means that the application should to be easy to use for the average person. This was tested by performing both hallway testing and remote usability testing.

\subsubsection{NFR2: The application's user interface should follow standard Android specifications for graphical user interfaces}
The target platform for the application is Android, which has a set of standards that aims to make its applications consistent. These standards makes it easier for a user to use a new application because they might feel familiar with the Android layout if they previously have used an Android device.
By running the usability test on Android users, the team got feedback from the test subjects on whether the app looked and behaved like an Android app.

\subsubsection{Test plan}
When a usability test is performed, the subjects are usually given a set of tasks to perform. During the test, the developers should take special note of whether the subjects are struggling or starts to get frustrated. The tasks the test subjects were to perform are presented in table~\ref{tab:usabilityTests}. 

For each task, the testers were asked the following questions:\\\\
1. What did you find complicating about the tasks given above?\\
2. Which of the above tasks did you find intuitive and easy to perform?\\
3. What features do you think should be added to make the tasks above easier?\\\\
The results from these tests may be found in appendix\todo{add test results in appendix}.

\begin{table}[H]
\rowcolors{0}{darkgray}{lightgray}
\centering
\begin{tabular}{|l|p{10.5cm}|}
\hline
\textbf{Task id }& \textbf{Task description}\\\hline
\textbf{1.}&\textbf{Basics}\\\hline
1.1 & Log in\\\hline
1.2 & View your profile\\\hline
1.3 & Add a new residence\\\hline
1.4 & Log out\\\hline
\textbf{2.}&\textbf{Devices}\\\hline
2.1 & Add a new device\\\hline
2.2 & Add usage to the device\\\hline
\textbf{3.}&\textbf{Usage}\\\hline
3.1 & Check the usage of the device called "Heater"\\\hline
3.2 & Compare the usage of your radio and TV\\\hline
\textbf{4.}&\textbf{Comparison}\\\hline
4.1 & Compare your usage with a friends\\\hline
4.2 & Compare your usage with someone with a similar profile\\\hline
\textbf{5.}&\textbf{Tips}\\\hline
5.1 & Add a tip to "my tips"\\\hline
5.2 & View your list of tips\\\hline
5.3 & Mark a tip as done\\\hline
\end{tabular}
\caption{Overview of usability test tasks}
\label{tab:usabilityTests}
\end{table}