\chapter{Further development}
\label{sec:further}
\section{}
\todo[inline]{Hardware solution}
In the very beginning of the project, the team looked into the possibility of getting live data directly from devices. This required some technical equipment for collecting and transmitting the usage of a device. The team were not able to find any cheap and easy way of doing this, so the idea was left. The concept was that the app should get live data directly form all of the devices in a house. It already exists hardware solutions that measures usage per device, but not that transmits that data wirelessly or via Bluetooth. If a hardware device doing both of these things is found, it is possible to modify Wattitude to get data from the hardware device. The next step would be that the devices transmits their energy usage directly by for instance Bluetooth. 

\subsection{The CoSSMic projects API}
Late in the project period, the team was made aware of an API that could be used to get data from devices. The team did not have time to implement together with or test this API in any way. But, to our understanding, this API provides data from devices, whether this is actual devices or dummy data, is not known. 

\section{Energy Production}
The team has implemented the possibility of creating a device with the category production. This was meant to be a category where all of a \todo[inline]{residence's} energy generating devices could be added. The customer wanted energy production to be in focus, and wanted the possibility of the users to not only monitor their consumption, but their energy production as well. 
\todo[inline]{Add more to this section}

\section{Gamification}
From the start, the customer uttered a wish of making the act of saving energy around your house, a contest of some sort. Through the concept of gamification. This was discussed within the team and a few different ideas came up. The general thought was that the user should feel that he achieved something, through saving energy and logging it within the app, and therefore would use the app to a greater extent. 

\subsection{Achievements}
One of the ideas that were discussed was the concept of achievement. That the user would get some sort of reward for achieving a saving goal, or conduct a saving tip in his residence. One of the ideas that came up was build on the achievement system that you find in the app "Untapped." \todo{Add reference to site}
This idea is based on a large base of "badges," or achievements that the user will get after doing something relevant and logging it within the app. 

Another achievement system that was discussed was to integrate different "Wattitude levels" into the app. The idea was to have one level per devotion to saving energy around your house. Say that the user has installed Wattitude \todo[inline]{Referance to each time it is mentioned?}, that gets him to the first level because he wants to be aware of his power consumption. And then, the idea moves on to several levels, for instance is level three to produce some energy yourself, to have tried at least five saving tips and to have shared your power consumption with your friends on Facebook. \todo[inline]{Add referance} Then, the user can say that his next goal is to reach "Wattitude level 3." \todo[inline]{Not very happy about this section. It is hard to write in past tense..}

\subsection{Wishlist}
\todo[inline]{This must be read through and reformulated}
To achieve some level of gamification, whether all amount of energy should also be displayed or translated into the equivalent amount of money. This makes room for another concept, namely that the user can create his own wishlists, with things he want, such as a vacation. And then, the app can display how much energy the user must save to equal the value of the thing he wants. To have a count down, of some sort, was also discussed. For instance, the app can display a status bar \todo[inline]{Find a better word?} which shows how many percent the user has managed to save or has left to save, to have saved the amount of energy equal to the value of the thing he wish for. Or it could display with the amount of energy that is saved in a given moment in comparison to an earlier moment, how long it will take for the user to save up the given amount of money.  


\section{Residences}
Maa kobles til alt

\section{Profile}
\todo[inline]{Must write something here}

\section{General}