\section{About the assignment}

The project is a part of an ongoing research program, CoSSMic~\cite{cossmic}, which focus on storage of renewable energy in private households. 
The idea is that entire neighborhoods should be able to benefit from the excess energy produced by other households in their neighborhood. 
The research program aims to develop the tools needed for this sharing of energy. 

The project's objective was to create an Android \gls{app}, making it possible for the user to monitor his\footnote{This report will use the term ''his'' to refer to ''his/her'' and ''he'' to refer to ''he/she''} 
energy usage and energy production. 

There exists similar apps on the market, some with complete systems to measure and control users' energy consumption. 
What they have in common is that they are either expensive, or they do not provide all the desired functionality. More details on this topic may be found in section~\ref{sec:altsolution}.
%None of the other solutions the team researched provide support for measuring the users' energy production, and likewise none of them allow for social integration. These solutions are further explained in section~\ref{sec:altsolution}.

The customer had a very clear idea on the concepts to be included in the app, though not much thought on the specifics. The team was provided with a figure that illustrated the most important concepts, which was used as foundation when the requirements were specified. 
%Based on this figure the team was to write a specification that could be adjusted in conjunction with the customer. 
This process is described further in section~\ref{sec:obtainingreq}.