\section{Functional requirements}
The functional requirements of a system is what the customer wants, made into concrete overall requirements to what functionality a system should include. These requirements are given in table~\ref{tab:funcReq}.

\todo{må legge til referanse til hvor disse kravene testes}
\begin{longtable}{|l|p{14.5cm}|}

\hline
\multicolumn{1}{|l|}{\textbf{ID}} &  \multicolumn{1}{c|}{\textbf{Description}}\\
\endfirsthead


\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\\hline
\multicolumn{1}{|l|}{\textbf{ID}} &  \multicolumn{1}{c|}{\textbf{Description}}\\
\endhead

\multicolumn{2}{|l|}{{Continued on next page}} \\ \hline
\endfoot
 
\endlastfoot

\hline
\cellcolor{lightgray}FR1 & \cellcolor{lightgray}Device control\\\hline
FR1.1. &The user should be able to see how much electricity each device in his house use on an average basis, on a monthly basis and on a yearly basis.\\\hline
FR1.2. &The user should be able to see how much electricity each device in his house produces on an average basis, on a monthly basis and on a yearly basis.\\\hline
FR1.3. &The user should be able to add new devices, and to specify whether a device produces or consumes power for each device.\\\hline
 FR1.4. &The user should be able to add the amount of power consumed\\\hline
FR1.5.& The user should be able to add the amount of power produced\\\hline
\cellcolor{lightgray}FR2. &\cellcolor{lightgray}Power usage\\\hline
FR2.1.& The app should show the user graphs over his usage over a predefined set timeframes chosen by the user.\\\hline
FR2.2.& The app should display a graph detailing the selected devices energy consumption.\\\hline
FR2.3.& The app should display a graph comparing the energy consumption from selected devices.\\\hline
\cellcolor{lightgray}FR3. &\cellcolor{lightgray}Energy saving tips\\\hline
FR3.1. &The user should have a list over the most used and best rated energy saving tips.\\\hline
FR3.2. &The user should be able to rate energy saving tips in a rating bar.\\\hline
FR3.3. &The user should have a list over what energy saving tips he has done.\\\hline
FR3.4.& The user will also be able to add energy saving tips he want to do in the future.\\\hline
FR3.5.& The user should be able to add new energy saving tips to the global list of energy saving tips.\\\hline
\cellcolor{lightgray}FR4.& \cellcolor{lightgray}Profile\\\hline
FR4.1.& The user should have his own personal profile\\\hline
FR4.2.& The user should be able to connect his Facebook profile to the app. The app should then retrieve information from Facebook to put in his profile.\\\hline
FR4.3. &The user should be able to specify whether or not his data should be used for statistics and comparisons.\\\hline
FR4.4.& The user should be able to choose which criterias he wants to use when comparing his energy usage with other people.\\\hline
\cellcolor{lightgray}FR5.& \cellcolor{lightgray}Social\\\hline
FR5.1. &The user should be able to share graphs on Facebook.\\\hline
FR5.2. &The user should be able to share energy saving tips on Facebook.\\\hline
FR5.3.& The app should contain a list with Facebook friends that uses the app.\\\hline
FR5.4.& The user should be able to compare his power usage with friends or users with similar profiles.\\\hline
\cellcolor{lightgray}FR6.& \cellcolor{lightgray}General\\\hline
FR6.1. & The app should be written so it is easy to add new languages.\\\hline FR6.2 & The app should use the language used on Android device. The default language, if Android language does not exist, is English\\\hline
\caption{Functional requirements}
\label{tab:funcReq}
\end{longtable} 
\begin{comment}
\subsection*{FR1. Device control}
\begin{itemize}
\item FR1.1. The user should be able to see how much electricity each device in his house use on an average basis, on a monthly basis and on a yearly basis.
\item FR1.2. The user should be able to see how much electricity each device in his house produces on an average basis, on a monthly basis and on a yearly basis.
\item FR1.3. The user should be able to add new devices 
\begin{itemize}
\item FR1.3.1. The user should be able to specify whether a device produces or consumes power for each device.
\end{itemize}
\item FR1.4. The user should be able to add the amount of power consumed
\item FR1.5. The user should be able to add the amount of power produced
\end{itemize}

\subsection*{FR2. Power usage}
\begin{itemize}
\item FR2.1. The app should show the user graphs over his usage over a predefined set timeframes chosen by the user.
\item FR2.2. The app should display a graph detailing the selected devices energy consumption.
\item FR2.3. The app should display a graph comparing the energy consumption from selected devices.
\end{itemize}

\subsection*{FR3. Energy saving tips}
\begin{itemize}
\item FR3.1. The user should have a list over the most used and best rated energy saving tips.
\item FR3.2. The user should be able to rate energy saving tips in a rating bar.
\item FR3.3. The user should have a list over what energy saving tips he has done.
\item FR3.4. The user will also be able to add energy saving tips he want to do in the future.
\item FR3.5. The user should be able to add new energy saving tips to the global list of energy saving tips.
\end{itemize}
\subsection*{FR4. Profile}
\begin{itemize}
\item FR4.1. The user should have his own personal profile
\item FR4.2. The user should be able to connect his Facebook profile to the app. The app should then retrieve information from Facebook to put in his profile.
\item FR4.3. The user should be able to specify whether or not his data should be used for statistics and comparisons.
\item FR4.4. The user should be able to choose which criterias he wants to use when comparing his energy usage with other people.
\end{itemize}

\subsection*{FR5. Social}
\begin{itemize}
\item FR5.1. The user should be able to share graphs on Facebook.
\item FR5.2. The user should be able to share energy saving tips on Facebook.
\item FR5.3. The app should contain a list with Facebook friends that uses the app.
\item FR5.4. The user should be able to compare his power usage with friends or users with similar profiles.
\end{itemize}


\subsection*{FR6. General}
\begin{itemize}
\item FR6.1. The app should be written so it is easy to add new languages
\begin{itemize}
\item The app should use the language used on Android device.
\item The default language, if Android language does not exist, is English
\end{itemize}
\end{itemize}
\end{comment}







