\chapter{Customer recommendation letter}

I have cooperated with group 16 in IT2901 in the role of customer
representing SINTEF. Our task was the development of a mobile
application to support awareness of own electricity consumption at
home. The task was related to a European project, called CoSSMic, led
by SINTEF that is about allowing private houses produce and consume
solar energy. Motivational apps have shown to have some effect in
changing habits and forming new habits. Our task was to create a
prototype that allowed users to become aware of their own consumption
patterns at home, and compare their own consumption to that of others
in similar situations. The prototype developed by the group will be
used as input to the development of an application in CoSSMic that
will be used in real-world trials in Germany and Italy later this
year.

Group 16 has worked in an organized way and we have had weekly
communication in form of Scrum meetings where in almost all of the
meetings I have been presented a new version of the application. We
have had fruitful discussions where I have learned tremendously and
our ideas at SINTEF have matured as a result. The application itself
has become an attractive result that can be used by its own and has a
potential in the market. I have got the impression that the group
dynamics have been good and all of the group members have contributed
to the discussions and to the results. It has been a pleasure to work
with group 16 and I hope we will have opportunities for cooperation in
the near future.